WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-22 article/Article.tex
cosmetics
darcs-hash:20060322160531-2fc9d-e9214ce8bd115ccee7e9b616575e65249b662c46.gz
add some references and use footnotes
darcs-hash:20060322165712-2fc9d-ea159a633e2c5739180dfbdf96895f0ea554d187.gz

\begin{abstract}
\noindent
ITK is a huge image analysis library, which contains lots of state of the arts
algorithms implementations. However, using it in C++ can be difficult and is
definitively bad suited for prototyping. WrapITK aims to allow classes from ITK
(and custom, classes that interact with ITK) to be "wrapped" for use with
languages like Python, Tcl, and Java.
\end{abstract}

@@

WrapITK is a project designed to allow classes from ITK (and custom, classes
that interact with ITK) to be "wrapped" for use with languages like
Python, Tcl, and Java.

Note that ITK already has a wrapping infrastructure. This project aims to be
address the following deficits of the existing wrappers (and others):
\begin{itemize}
  \item  ITK is a huge library, but only a small number of classes are available
in target languages. It become quickly frustrating for the user, especially when
he has to spend lot of time to extend the current set of classes. Even if it is
not yet complete, the WrapITK's set of classes have been highly extended. Moreover,
the user can choose at build time which types and which dimensions he want to wrap.

@@

For the user which don't want to use darcs but want the last development version,
a nightly updated archive is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.

@@

  \item \verb$itk.auto_progress( b )$ is used to automatically add a progress report
to all the newly created filters. \verb$b$ must be \verb$True$ or \verb$False$. If
\verb$b$ is true, something like
\begin{verbatim}
9> median.Update()
itkMedianImageFilterIF2IF2: 0.109990
\end{verbatim}
is displayed on the standard output. 
While prototyping, it is a convenient way for the user to know if
the execution time will be short or if he can do something more useful than waiting
for the filter to complete (like having a cup of tea).

@@

WrapITK is an opensource project, and so all contributions are welcome. Here are
some points which requires special attention:
\begin{itemize}
  \item Test it and report problem. That's the more important thing to do:
we need feedbacks to enhance WrapITK quality !
  \item Work on tcl, java, and others. We are not tcl or java developers, and so
are not able to complete the work for those languages. Any help from tcl and
java expert would be highly appreciated. Also, there is no reason to be limited
to python, tcl and java, and WrapITK can be extended to other languages supported
by swig like perl, ruby, ocaml and others.
  \item Add more classes. WrapITK add lots of new classes compared to the current
wrapping system, but there is still lots of work to do, especially to support more
filter dedicated to \verb$Vector$ pixels.
\end{itemize}

\verb$darcs$ allow to easily contribute to WrapITK, by sending patch by email with
the command \verb$darcs send$, while keeping credits for the work done.
Feel free to send patches; they will be tested and integrated in the project.

A web interface (\url{http://auriga.wearlab.de/~alb/darcsweb/}) for the WrapITK darcs
repository is available at \url{http://voxel.jouy.inra.fr/darcsweb/}.

@@

Thank to Charl P. Botha for is help to debug WrapITK on windows plateform and for the
patches he has contributed.

@@

% \url{http://www.itk.org}
% \code{Insight/Documentation/Style.pdf}
% \section{Principles of Solar Spot Detection}
% \cite{ITKSoftwareGuide}.
% \doxygen{ImageToImageFilter}

% \small \begin{verbatim}
% \end{verbatim} \normalsize

% The {itemize} environment uses a bullet for each \item.  If you want the 
% \item's numbered, use the {enumerate} environment instead.
% \begin{itemize}
%   \item  Insight Toolkit 2.4.
%   \item  CMake 2.2
% \end{itemize}

% \ref{cthead1}

% \begin{figure}[htbp]
% \centering
% \includegraphics{cthead1}
% \caption{The input image.\label{cthead1}}
% \end{figure}

@@

\bibliographystyle{plain}
\bibliography{InsightJournal}
\nocite{ITKSoftwareGuide}

>>>>

\begin{abstract}
\noindent
ITK \cite{ITKWebSite} is a huge image analysis library, which contains lots of state of the arts
algorithms implementations. However, using it in C++ can be difficult and is
definitively bad suited for prototyping. WrapITK aims to allow classes from ITK
(and custom, classes that interact with ITK) to be "wrapped" for use with
languages like Python \cite{PythonWebSite}, Tcl \cite{TclWebSite}, and Java \cite{JavaWebSite}.
\end{abstract}

@@

WrapITK is a project designed to allow classes from ITK (and custom, classes
that interact with ITK) to be "wrapped" for use with languages like
Python \cite{PythonWebSite}, Tcl \cite{TclWebSite}, and Java \cite{JavaWebSite}.

Note that ITK already has a wrapping infrastructure, and that WrapITK is based
on it, and use the same tools: CMake \cite{CMakeWebSite}, GCC-XML \cite{GccxmlWebsite}
and CableSwig \cite{CableSwigWebSite}. This project aims to be
address the following deficits of the existing wrappers (and others):
\begin{itemize}
  \item  ITK is a huge library, but only a small number of classes are available
in target languages. It become quickly frustrating for the user, especially when
he has to spend lot of time to extend the current set of classes. Even if it is
not yet complete, the WrapITK's set of classes have been highly extended. Moreover,
the user can choose at build time which types and which dimensions he want to wrap.

@@

For the user which don't want to use darcs \cite{DarcsWebSite} but want the last development version,
a nightly updated archive is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.

@@

  \item \verb$itk.auto_progress( b )$ is used to automatically add a progress report
to all the newly created filters. \verb$b$ must be \verb$True$ or \verb$False$. If
\verb$b$ is true, something like
\begin{verbatim}
9> median.Update()
itkMedianImageFilterIF2IF2: 0.109990
\end{verbatim}
is displayed on the standard output. 
While prototyping, it is a convenient way for the user to know if
the execution time will be short or if he can do something more useful
\footnote{like having a cup of tea} than waiting for the filter to complete.

@@

WrapITK is an opensource project, and so all contributions are welcome. Here are
some points which requires special attention:
\begin{itemize}
  \item Test it and report problem. That's the more important thing to do:
we need feedbacks to enhance WrapITK quality !
  \item Work on tcl, java, and others. We are not tcl or java developers, and so
are not able to complete the work for those languages. Any help from tcl and
java expert would be highly appreciated. Also, there is no reason to be limited
to python, tcl and java, and WrapITK can be extended to other languages supported
by swig like perl \cite{PerlWebSite}, ruby \cite{RubyWebSite}, ocaml \cite{OcamlWebSite} and others.
  \item Add more classes. WrapITK add lots of new classes compared to the current
wrapping system, but there is still lots of work to do, especially to support more
filter dedicated to \verb$Vector$ pixels.
\end{itemize}

\verb$darcs$ \cite{DarcsWebSite} allow to easily contribute to WrapITK, by sending patch by email with
the command \verb$darcs send$, while keeping credits for the work done.
Feel free to send patches; they will be tested and integrated in the project.

A web interface \cite{DarcswebWebSite} for the WrapITK's darcs
repository is available at \url{http://voxel.jouy.inra.fr/darcsweb/}.

@@

We thank Charl P. Botha for is help to debug WrapITK on windows plateform, and for the
patches he has contributed.

@@

@@

\bibliographystyle{plain}
\bibliography{Article,InsightJournal}
\nocite{ITKSoftwareGuide}
